%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {AIMS Lab (Advisor: Dr. Srikanth Divi)} % Organization
    {Manipal Institute of Technology} % Institute
    {Manipal, India} % Location
    {Apr. 2024 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Investigating diverse topics using molecular and particle transport simulation techniques.}
        \item {Utilized the Schrödinger Maestro MS suite extensively for tasks including building models, setting up and executing simulations, analyzing properties, and visualizing results.}
        \item {Calculated key physical properties to understand system behavior across different projects.}
        \item {Focused efforts on the SEI project, simulating and analyzing SEI formation, reaction mechanisms and comparing different electrolyte/electrode systems to identify favorable interface characteristics.}
        \item {Explored automated chemical kinetic model generation using Reaction Mechanism Generator for potential application to electrolyte decomposition pathways.}
        \item {Preparation of a project investigating SEI formation on next-generation electrodes and electrolytes.}
        \item {Developing models and performing Monte Carlo simulations for a comparative study on fission reactors using OpenMC.} 
        \item {Analyzing OpenMC simulation data to create a reactor class surrogate model.}
        \item {Preparing results from OpenMC project for an intended arXiv preprint submission.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Cavitation Process Engineering Lab (Advisor: Dr. Jitendra Carpenter)} % Organization
    {Manipal Institute of Technology} % Institute
    {Manipal, India} % Location
    {Dec. 2023 - Apr. 2024} % Date(s)
    {
      \begin{cvitems}
        \item {Investigated the stability of curcumin-based emulsions for potential drug delivery applications.}
        \item {Investigated the stability of curcumin-based emulsions for potential drug delivery applications.}
        \item {Prepared nanoemulsions with varying compositions using ultrasonication techniques.}
        \item {Monitored emulsion degradation and assessed stability over time through UV spectroscopy analysis.}
    }
%---------------------------------------------------------
\end{cventries}
