%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects and Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Project / Preprint} % Role
    {Monte Carlo Simulations and Surrogate Modeling of Fission Reactors using OpenMC}
    {Arya Goyal} % Event % Location
    {Advisor: Dr. Srikanth Divi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developing OpenMC models to simulate fission reactor systems.}
        \item {Analyzing and comparing reactor neutronics and performance data.}
        \item {Implementing and refining surrogate modeling techniques to create computationally effecient representations of simulation results.}
        \item {Work in progress. Preprint detailing methodology and initial findings is currently in preparation for submission to arXiv.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Paper} % Role
    {Investigation of Solid Electrolyte Interphase Formation via Molecular Dynamics} % Event
    {Arya Goyal, Chakradhar Polu} % Location
    {PI: Dr. Srikanth Divi} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created systems using combinations of conventional and novel electrolyte and electrode materials.}
        \item {Completed molecular dynamics simulations Maestro MS investigating SEI formation mechanisms at the anode.}
        \item {Analyzed simulation results to characterize SEI structure, composition, and ion transport properties.}
        \item {Finalizing manuscript detailing simulation results and analysis, expected  completion by mid-November 2025.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}